---
title: "iterate_ways"
output: 
  html_document:
    toc : true
    toc_float: true
---

```{r setup, include=FALSE}
library(tidyverse)
```

This illustrates ways to do iteration in R. 

# simulated dataset

```{r simulate}
# generate a 30x3 matrix
set.seed(2)
s_matrix = cbind(rnorm(30, 0), rnorm(30, 2), rnorm(30, 5))

# genertate a date frame with the same data
set.seed(2)
s_df = tibble(a = rnorm(30, 0), b = rnorm(30, 2), c = rnorm(30, 5))
```


# apply

```{r apply}
# return row means, 1 indicate row
apply(s_matrix, 1, mean)   # return numeric vector
apply(s_df, 1, mean)       # return named numeric vector

# return column means, 2 indicate column
apply(s_matrix, 2, mean)   
apply(s_df, 2, mean)

# use map family
map(s_df, mean)  # return list 
map(s_matrix, mean)  # NOT working for matrix, iterates on every cell and return a list with length 90.

map_dfr(s_df, mean)

# define my own function to return number of negative values in each column
apply(s_matrix, 2, function(x) length(x[x<0]))
map(s_df, function(x) length(x[x<0]))
map(.x = s_df, ~length(.x[.x<0]))   # handy 


# define my own function to return mean and sd in each column 
mean_sd = function(x){
  tibble(mean = mean(x),
         sd = sd(x))
}

# use map family 
map(s_df, mean_sd) # return list 

map_dfr(s_df, mean_sd, .id = "input")  # return df by row binding 
map(s_df, mean_sd) %>% bind_rows(.id = "input") # equivalent
map_dfr(s_df, ~tibble(mean = mean(.x), sd = sd(.x)), .id = "input") # equivalent

map_dfc(s_df, mean_sd)  # return df by column binding, bind_cols has no parapeter of .id
map(s_df, mean_sd) %>% bind_cols() # equivalent

# use apply 
apply(s_matrix, 2, mean_sd)  # return list 
apply(s_df, 2, mean_sd) # return list, the same as map

```

`apply`is mainly for matrix (df works too). It can work on columns or rows and returns either vector or list.
`apply` doesn't work for vector or list, as it requires `dim` to be positve. 

map doesn't work on rows and returns always lists. map is more specialized on df and can write functions in a simple way.


# sapply and lapply

```{r }
# return a list 
lapply(1:3, function(x) x^2)
map(1:3, ~.x^2)        # equivalent 
sapply(1:3, function(x) x^2, simplify=F)  # equivalent

# return a vector
sapply(1:3, function(x) x^2)

```
